### 2023-04-07 main.tex
RD

\subsection{Linear reaction-diffusion process with coupled discrete Laplacians}

@@

    \mathcal{L}_{x,y}^{rd}=\sigma_{11}\mathcal{L}_{x,y}+\sigma_{12}\sum_{c=1}^{N}\mathcal{L}_{x,y}^{c}+(\Upsilon-2\nu\sigma_{12})\mathcal{L}_{x,y}^{m}
with $\mathcal{L}_{x,y}$ is the generator the generator \eqref{edgeGenerator} and, for any function $f:\Omega\to \mathbb{R}$

@@

@@

    k+c-N\quad &\text{if}\quad k+c>N\\

@@

\end{cases}\qquad \forall k\in \{1,\ldots N\}

@@

	\alpha_{a}^{x}&=\sigma_{11}\nu\rho_{a}^{x}+\sigma_{12}\nu\sum_{b=2\,:\,b\neq a}^{N}\rho_{b}^{x}\qquad \text{if} \quad k\in \{2,\ldots,N\}\\
	\alpha_{1}^{x}&=\nu\left(\sigma_{11}+(N-1)\sigma_{12}\right)-\sum_{a=2}^{N}\alpha_{a}^{x}
\paragraph{Action on the occupation variable $n_{d}^{x}$ for the edge generator $\mathcal{L}_{x,y}^{rd}$}
The action on the occupation variable $n_{d}^{x}$ of particle type $d\in \{2,\ldots,N\}$ at site $x\in V $
is the following 

@@

    \mathcal{L}_{x,y}^{rd}n_{d}^{x}&=\nu \sigma_{11}(n_{d}^{y}-n_{d}^{x})+\nu\sigma_{12}\sum_{c=2\,:	,c\neq d}^{N}(n_{c}^{y}-n_{d}^{x})+(\Upsilon-2\nu\sigma_{12})\sum_{c=2}^{N}(n_{c}^{x}-n_{\alpha}^{x})

@@

while for every $c\in \{2,\ldots,N\}$ we have 
\mathcal{L}_{x,y}^{c}n_{a}^{x}&=\sum_{a,b=1}^{N}n_{a}^{x}n_{b}^{y}\left((n_{d}^{x}-\delta_{a}^{x}+\delta_{g_{c}(b)}^{x}+\delta_{g_{c}(a)}^{y}-\delta_{b}^{y})-n_{\alpha}^{x}\right)=\sum_{a=1}^{N}n_{a}^{x}n_{q}^{y}-\sum_{\ell=1}^{N}n_{\alpha}^{x}n_{\ell}^{y}
\sum_{a=2}^{N}n_{a}^{x}n_{q}^{y}-\left(\nu-\sum_{i=2}^{N}n_{i}^{x}\right)n_{q}^{y}-\sum_{\ell=2}^{N}n_{\alpha}^{x}n_{\ell}^{y}-n_{\alpha}^{x}\left(\nu-\sum_{i=2}^{N}n_{i}^{y}\right)
\nu(n_{q}^{y}-n_{\alpha}^{x})
where we call $q\in \{2,\ldots,N\}$ such that $g_{i}(q)=\alpha$ and $\ell\in \{2,\ldots,N\}$ such that $g_{i}(\ell)\neq \alpha$.

@@

Then, summing over all indices $c\in\{2,\ldots,N\}\,:\,c\neq d$, we obtain \eqref{actionGraphRD}.
\paragraph{Action on the occupation variable $n_{d}^{x}$ for the site generator $\mathcal{L}_{x}^{rd}$}

@@

@@

	\alpha_{d}^{x}\left(\nu-n_{d}^{x}\right)-n_{d}^{x}\left(\nu(\sigma_{11}+(N-1)\sigma_{12})-\alpha_{d}^{x}\right)
As a consequence, considering \eqref{actionGraphRD} on the geometry of a chain of finite length $L\in \mathbb{N}$, the action of the generator \eqref{RDGenerator} on the occupation variable $n_{\alpha}^{x}$ gives

@@

\mathcal{L}^{rd}n_{d}^{x}=\nu\sigma_{11}\Delta_{L}n_{d}^{x}+\nu\sigma_{12}\sum_{c=2\,:\,l\neq d}^{N}\Delta_{L}n_{c}^{x}+\Upsilon\sum_{c=2}^{N}(n_{c}^{x}-n_{\alpha}^{x})
where with the symbol $\Delta_{N}$ we denote the discrete Laplacian operator on the chain, i.e. $\Delta_{L}n_{a}^{x}=n_{a}^{x+1}+n_{a}^{x-1}-2n_{a}^{x}$, $\forall x\in \{2,\ldots,L-1\}$ and $\forall a\in \{2,\ldots,N\}$. In the spirit of \cite{casini2022uphill} we can write he the Master's equation for the evolution of the average density occupation, obtaining a system of $N-1$ difference differential equation where the discrete Laplacian of all species are coupled and linear reaction term are present. 

@@

The process defined by generator \eqref{RDGenerator} has reversible product measure when all the reservoirs have the same parameter for each site and each species, i.e. $\alpha_{a}^{x}=\alpha$, $\forall a\in \{1,\ldots,N\}$ and $x\in V$. This measure is given by
    \Lambda^{rev}=\bigotimes_{x\in V}\Lambda_{x}^{rev}
where the marginals are
    \Lambda_{x}^{rev}\sim \text{Multinomial}(\nu,p,\ldots,p)
with $p=\frac{1}{N}$. This can be verified by imposing the detailed balance condition.

@@

This generator $\mathcal{L}^{rd}$ can be described by the Hamiltonian $H^{rd}$ that is defined through the basis elements \eqref{actionE} of the $gl(N)$ Lie algebra as 
    H^{rd}=\sum_{x,y\in \mathcal{E}}\omega_{x,y}\left(\sigma_{11}H_{x,y}+\sigma_{12}\sum_{c=1}^{N}H_{x,y}^{c}+(\Upsilon-2\sigma_{12})H_{x,y}^{m}\right)+\sum_{x\in V}\Gamma_{x}H_{x}

@@

    H_{x,y}^{m}=\sum_{a,l}^{N}\left(E_{la}^{x}\otimes \mathbbm{1}^{y}-E_{aa}^{x}\otimes \mathbbm{1}^{y}\right)
For this model, the duality relation is

@@

where the duality matrix $D$ is again \eqref{dualityMatrix}. Following subsection~\ref{subsectionDualityProof}, to prove \eqref{DualityRelationRD} we only need tho show that the operator $S_{x,y}$ defined in \eqref{symmetry} commutes with $\sum_{i=1}^{N}H_{x,y}^{x}$ and with $H_{x,y}^{m}$. This result will follow from the commutator between $\sum_{i=1}^{N}H_{x,y}^{x}$ and $\sum_{a=2}^{N}(E_{a1}^{x})\otimes \sum_{b=2}^{N}E_{b,1}^{x}$ and from the commutator between  and $\sum_{a=2}^{N}(E_{a1}^{x})\otimes \sum_{b=2}^{N}E_{b,1}^{x}$. Using \eqref{eq:comgl}, the bilinearity and associativity of the Kronecker product and the bilinearity of the brackets we obtain 
    &\left[\sum_{a=2}^{N}E_{a1}^{x}\otimes \sum_{b=2}^{N}E_{b1}^{x},\;\sum_{i=1}^{N}\sum_{a,l=1}^{N}\left(E_{g_{i}(l)a}^{x}\otimes E_{g_{i}(k)l}^{y}-E_{aa}^{x}\otimes E_{ll}^{y}\right)\right]
    \\=&\sum_{a,b=2}^{N}\sum_{i=1}^{N}\sum_{a,l=1}^{N}\left\{\left(E_{aa}^{x}\delta_{g_{i}(l)0}-E_{g_{i}(l)0}^{x}\delta_{aa}\right)\otimes \left(E_{bl}^{y}\delta_{g_{i}(k)0}-E_{g_{i}(k)0}^{y}\delta_{ba}\right)-\left(E_{aa}^{x}\delta_{a0}-E_{a0}^{x}\delta_{aa}\right)\otimes \left(E_{bl}^{y}\delta_{l0}-E_{l0}^{y}\delta_{bl}\right)\right\}

@@

    \sum_{a,b=2}^{N}\sum_{i=1}^{N}\sum_{a,l=1}^{N}\left(E_{aa}^{x}\left(\delta_{g_{i}(l)0}-\delta_{a0}\right)-\left(E_{g_{i}(l)0}^{x}-E_{a0}^{x}\right)\delta_{aa}\right)\otimes \left(E_{bl}^{y}\left(\delta_{g_{i}(k)0}-\delta_{l0}\right)-\left(E_{g_{i}(k)0}^{y}-E_{l0}^{y}\right)\delta_{bl}\right)
    \\=&\;0
 Again, using \eqref{eq:comgl} and by a similar argument, we obtain

@@

Therefore, arguing similarly to subsection~\ref{subsectionDualityProof}, \eqref{DualityRelationRD} can be proved.

>>>>

\subsection{Linear reaction-diffusion process on a finite graph}

@@

\begin{equation}\label{edgeGeneratorRD}
    \mathcal{L}_{x,y}^{rd}=\sigma_{11}\mathcal{L}_{x,y}+\sigma_{12}\sum_{c=1}^{N-2}\mathcal{L}_{x,y}^{c}+(\Upsilon-2\nu\sigma_{12})\mathcal{L}_{x,y}^{m}
with $\mathcal{L}_{x,y}$ is the edge \eqref{edgeGenerator} of the multi-species stirring process and, for any function $f:\Omega\to \mathbb{R}$ and for any $c\in \{1,\ldots,N-2\}$

@@

	g_{c}(\cdot):\{1,\ldots,N\}&\to\{1,\ldots,N\}\\
	k&\to g_{c}(k)
defined $\forall c\in\{1,\ldots,N-2\}$ as 

@@

    k+c-N+1\quad &\text{if}\quad k+c>N\\

@@

Observe that $g_{c}(\cdot)$ is surjective and bijective, and thus invertible. \\
Moreover,

@@

	\alpha_{a}^{x}&=\sigma_{11}\rho_{a}^{x}+\sigma_{12}\sum_{b=2\,:\,b\neq a}^{N}\rho_{b}^{x}\qquad \text{if} \quad k\in \{2,\ldots,N\}\\
	\alpha_{1}^{x}&=\nu\left(\sigma_{11}+(N-2)\sigma_{12}\right)-\sum_{a=2}^{N}\alpha_{a}^{x}
and where, for every $x\in V$, we further assume that
	\sum_{a=1}^{N}\rho_{a}^{x}=\nu
\textbf{Remark}: observe that the site generator $\mathcal{L}_{x}^{rd}$ is exactly the one of the multi-species stirring process \eqref{siteGenerator}. We wrote it with the uppercase 'rd' in order to underline the fact that we need a specific choice of the reservoirs parameters $\alpha_{a}^{x}$, as specified above. 
\paragraph{Action on the occupation variable of the edge generator}
For arbitrary edge $(x,y)\in \mathcal{E}$, the action on the occupation variable $n_{d}^{x}$ of particle of type $d\in \{2,\ldots,N\}$ at site $x\in V $ of the edge generator $\mathcal{L}_{x,y}^{rd}$ reads

@@

    \mathcal{L}_{x,y}^{rd}n_{d}^{x}&=\nu \sigma_{11}(n_{d}^{y}-n_{d}^{x})+\nu\sigma_{12}\sum_{q=2\,:	,q\neq d}^{N}(n_{c}^{y}-n_{d}^{x})+(\Upsilon-2\nu\sigma_{12})\sum_{b=2}^{N}(n_{b}^{x}-n_{\alpha}^{x})

@@

while for every $c\in \{1,\ldots,N-2\}$ we have 
\mathcal{L}_{x,y}^{c}n_{d}^{x}&=\sum_{a,b=1}^{N}n_{a}^{x}n_{b}^{y}\left((n_{d}^{x}-\delta_{a}^{x}+\delta_{g_{c}(b)}^{x}+\delta_{g_{c}(a)}^{y}-\delta_{b}^{y})-n_{d}^{x}\right)=\sum_{a=1}^{N}n_{a}^{x}n_{q}^{y}-\sum_{\ell=1}^{N}n_{d}^{x}n_{\ell}^{y}
\sum_{a=2}^{N}n_{a}^{x}n_{q}^{y}-\left(\nu-\sum_{i=2}^{N}n_{i}^{x}\right)n_{q}^{y}-\sum_{\ell=2}^{N}n_{d}^{x}n_{\ell}^{y}-n_{d}^{x}\left(\nu-\sum_{i=2}^{N}n_{i}^{y}\right)
\nu(n_{q}^{y}-n_{d}^{x})
where we call $q$ such that $g_{i}^{-1}(d)=q$. Let us observe that, by the definition of the map $g_{c}(\cdot)$ and for the fact that $1\leq c\leq N-2$, $q\neq d$ and $q\neq 1$ .

@@

Then, summing over all indices $c\in\{1,\ldots,N-2\}$, we obtain \eqref{actionGraphRD}.
\paragraph{Action on the occupation variable of the site generator}

@@

\begin{equation}\label{actionBoudaryRD}

@@

	\alpha_{d}^{x}\left(\nu-n_{d}^{x}\right)-n_{d}^{x}\left(\nu(\sigma_{11}+(N-2)\sigma_{12})-\alpha_{d}^{x}\right)
	\\&=\alpha_{d}^{x}\nu-n_{d}^{x}\nu(\sigma_{11}+(N-2)\sigma_{12})
	\nu\sigma_{11}\rho_{d}^{x}+\nu\sigma_{12}\left(\sum_{b=2\,:\,b\neq d}^{N}\rho_{b}^{x}\right)-n_{d}^{x}\nu(\sigma_{11}+(N-2)\sigma_{12})
\subsection{Reaction-diffusion process on a chain}
Here we consider the geometry of a chain of length $L$ with two reservoirs connected with the end sites $1$ and $L$. This geometry is the same used in section \ref{sectionIntegrabiliy}, but now the occupation variable is arbitrary and denoted by $\nu\in \mathbb{N}$.\\
Using equation \eqref{actionGraphRD} we have that $\forall x\in \{2,\ldots,L-1\}$ and $\forall d\in\{2,\ldots,N\}$

@@

\mathcal{L}^{rd}n_{d}^{x}=\nu\sigma_{11}\Delta_{L}n_{d}^{x}+\nu\sigma_{12}\sum_{c=2\,:\,c\neq d}^{N}\Delta_{L}n_{c}^{x}+\Upsilon\sum_{c=2}^{N}(n_{c}^{x}-n_{\alpha}^{x})
where with the symbol $\Delta_{L}$ we denote the discrete Laplacian operator on the chain, i.e. $\Delta_{L}n_{a}^{x}=n_{a}^{x+1}+n_{a}^{x-1}-2n_{a}^{x}$.
Similarly, using \eqref{actionGraphRD}  and \eqref{actionBoudaryRD} we have that, $\forall d\in \{2,\ldots,N\}$ 
\mathcal{L}^{rd}n_{d}^{1}=\sigma_{11}\nu \left(\rho_{d}^{1}-2n_{d}^{1}+n_{2}^{2}\right)+\sigma_{12}\nu\sum_{c=2\,:\,c\neq d}^{N}\left(\rho_{c}^{1}-2n_{c}^{1}+n_{c}^{2}\right)+\Upsilon\sum_{c=2\,:\,c\neq d}^{N}\left(n_{c}^{1}-n_{d}^{1}\right)
On the occupation variable $n_{d}^{L}$ the action is similar, but with the upper case $1$ replaced by $L$
 In the spirit of \cite{casini2022uphill} we can write he the Master's equation for the evolution of the average density occupation, obtaining a system of $N-1$ difference-differential equation where the discrete Laplacians of all species are coupled and linear reaction terms are present. Therefore, this model is a generalization to $N$ species and to maximal occupation $\nu$ of the one studied in \cite{casini2022uphill}. This answers the first question of the beginning of this section. 

@@

The process described by the generator \eqref{RDGenerator} is reversible with respect to the homogeneus product measure \begin{equation}\label{reversibleMeasureRD}
	\Lambda_{rev}=\bigtimes_{x\in V}\Lambda_{rev}^{x}
\begin{equation}\label{reversibilityConditionRD}
This measure has marginals $\Lambda_{rev}^{x}$ given by 
	\Lambda^{x}_{rev}\sim \text{Multinomial}\left(\twoj,\rho_{1},\ldots,\rho_{N}\right)\quad \text{where}\quad \rho_{a}=\frac{1}{N}
	\Lambda_{rev}^{x}(n^{x})=\frac{\nu!}{\prod_{a=1}^{N}n_{a}^{x}!}\left(\frac{1}{N}\right)^{\sum_{a=1}^{N}n_{a}^{x}}
This can be proved just by imposing the detailed balance conditions for the edge and for the site generators. For fixed edge $(x,y)\in \mathcal{E}$ and $x\in V$ the detailled balances for $\mathcal{L}_{x,y}$ and for $\mathcal{L}_{x}$ are analogous, while for $\mathcal{L}_{x,y}^{c}$ with $c\in\{1,\ldots,N-2\}$ we have the following. Consider the transition $\bm{n}\to \bm{n}-\delta_{a}^{x}+\delta_{g_{c}(b)}^{x}+\delta_{g_{c}(b)}^{y}-\delta_{b}^{y}$; the detailled balance reads
		&n_{a}^{x}n_{b}^{y}\frac{\nu!}{n_{1}^{x}!\cdots n_{a}^{x}!\cdots n_{g_{c}(b)}^{x}!\ldots n_{N}^{x}!}\frac{\nu!}{n_{1}^{y}!\cdots n_{b}^{y}!\cdots n_{g_{c}(a)}^{y}!\ldots n_{N}^{y}!}\\&\rho_{1}^{n_{1}^{x}+n_{1}^{y}}\cdots \rho_{a}^{n_{a}^{x}}\cdots\rho_{g_{c}(b)}^{n_{g_{c}(b)}^{x}}\cdots\rho_{b}^{n_{b}^{y}}\cdots \rho_{g_{c}(a)}^{n_{g_{c}(a)}^{y}}
		\\
		=&(n_{g_{c}(b)}^{x}+1)(n_{g_{c}(a)}^{y}+1)\frac{\nu!}{n_{1}^{x}!\cdots (n_{a}^{x}-1)!\cdots (n_{g_{c}(b)}^{x}+1)!\ldots n_{N}^{x}!}\frac{\nu!}{n_{1}^{y}!\cdots (n_{b}^{y}-1)!\cdots (n_{g_{c}(a)}^{y}+1)!\ldots n_{N}^{y}!}
		\rho_{1}^{n_{1}^{x}+n_{1}^{y}}\ldots \rho_{a}^{n_{a}^{x}-1}\cdots\rho_{g_{c}(b)}^{n_{g_{c}(b)+1}^{x}}\cdots\rho_{b}^{n_{b}^{y}-1}\cdots \rho_{g_{c}(a)}^{n_{g_{c}(a)-1}^{y}}
that simplifies to 
	\rho_{a}\rho_{b}=\rho_{g_{c}(b)}\rho_{g_{c}(a)}
that is true if and only if $p_{a}=p$ $\forall a\in \{2,\ldots,N\}$.\\
By similar computation it is possible to show that the same result is obtained imposing the detailled balance for the transition $\bm{n}\to \bm{n}-\delta_{a}^{x}+\delta_{b}^{x}$. \\
Recalling that, to have reversibility the reservoirs parameters must fulfil $\rho_{a}^{x}=\rho_{a}$ $\forall x \in V$ and $\forall a\in \{1,\ldots,N\}$, we obtain the result. 

@@

In this subsection we formulate duality for the multi-species stirring process $(\mathbf{n}(t))_{t\geq 0}$, defined by the generator \eqref{RDGenerator}.
The dual  process $(\bm{\xi}(t))_{t\geq 0}$ takes values in the enlarged state space
	\widetilde{\Omega}= \bigtimes_{x\in V} \widetilde{\Omega}_{x}\ = \bigtimes_{x\in V} (\Omega_{x}\times \mathbb{N}_{0}^{N-1})
To each site $x\in V$ we associate an ``extra site'', denoted $\widehat{x}$,
where dual particles will accumulate in the course of time. 
We write the configurations $\bm{\xi} \in \widetilde\Omega$  as
	\bm{\xi}=\left(r_{1}^{x},\ldots,r_{N}^{x},m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}\right)_{x\in V}
where the component $r_{a}^{x}$ is interpreted as the number of dual particles of type $a\in \{1,\ldots,N\}$ at site $x$, 
and the component $m_{a}^{\widehat{x}}$  gives the number of dual particles of type $a\in \{2,\ldots,N\}$ at 
the extra-site $\widehat{x}$ connected to $x\in V$.

The duality function is given by
	D(\bm{n},\bm{\xi})=\prod_{x\in V}\left(\frac{(\nu -\sum_{a=2}^{N}r_{a}^{x})!}{\nu!}\prod_{a=2}^{N}\frac{n_{a}^{x}!}{(n_{a}^{x}-r_{a}^{x})!}\left(\rho_{a}^{x}\right)^{m_{a}^{\widehat{x}}}\,\right)
%where we denote the \textit{density} of the species $a\in \{2,\ldots,N\}$ imposed by the reservoir at site $x\in V$  by 
%	\rho_{a}^{x}:=\frac{\alpha_{a}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}
The dual process is defined by its generator, which reads
\begin{equation}\label{DualGenerator}
	\widetilde{\mathcal{L}}=\sum_{(x,y)\in \mathcal{E}}\omega_{x,y}\mathcal{L}_{x,y}^{rd}+\sum_{x\in V}\Gamma_{x}\widetilde{\mathcal{L}}_{x}^{rd}
$\mathcal{L}_{x,y}^{rd}$ is defined in \eqref{edgeGeneratorRD} and, $\widetilde{\mathcal{L}}_{x}^{rd}$ is again the absorbing dual generator $\widetilde{\mathcal{L}}_{x}$ defined in \eqref{siteDualGenerator}. 
\textbf{Remark}: the generator $\mathcal{L}^{rd}$ has a dual with respect to the same duality function of $\mathcal{L}$ of the multi-species stirring process. Moreover, the dual process has absorbing boundaries while it performs the same edge dynamics of $\mathcal{L}^{rd}$. As we will show this follows from the same $gl(N)$ algebraic structure. 
\subsubsection{Proof of duality relation for reaction-diffusion process}
In the spirit of what we did in Section \ref{sectionDuality}, it is convenient to write the Hamiltonian of the process, that is defined through the basis elements \eqref{actionE} of the $gl(N)$ Lie algebra as 
    H^{rd}=\sum_{x,y\in \mathcal{E}}\omega_{x,y}\left(\sigma_{11}H_{x,y}+\sigma_{12}\sum_{c=1}^{N-2}H_{x,y}^{c}+(\Upsilon-2\sigma_{12})H_{x,y}^{m}\right)+\sum_{x\in V}\Gamma_{x}H_{x}

@@

    H_{x,y}^{m}=\sum_{a,b=1}^{N}\left(E_{ba}^{x}\otimes \mathbbm{1}^{y}-E_{aa}^{x}\otimes \mathbbm{1}^{y}\right)
Similarly, we define the dual Hamiltonian $\widetilde{H}^{rd}$. For the edge dynamics, the original and the dual Hamiltonians do coincide, while the site one it is again $\widetilde{H}_{x}$ defined in \eqref{siteDualHamiltonian}. \\ We aim to show

@@

Therefore, we need to prove that
	(H_{x,y}^{rd})^{T}D&=DH_{x,y}^{rd}\label{edgeDualityRelationRD}\\
	H_{x}^{T}D&=D\widetilde{H}_{x}D\label{siteDualityRelationRD}
where the duality matrix $D$ is again \eqref{dualityMatrix}. As already pointed out, $H_{x}$ and $\widetilde{H}_{x}$ are the same of the stirring process, while $H_{x,y}^{rd}$ has two more terms $\sum_{c=1}^{N-2}H_{x,y}^{c}$ and $H_{x,y}^{m}$. Therefore, we only need to show that 
	&(H_{x,y}^{c})^{T}D=DH_{x,y}^{c}\qquad \forall c\in \{1,\ldots,N-2\}\label{cDualityRelation}\\
	&(H_{x,y}^{m})^{T}D=DH_{x,y}^{m}\label{mDualityRelation}
Since the matrix $R_{x}$ is the same, we shall show that $H_{x,y}^{c}$ and $H_{x,y}^{m}$ are symmetries of $\exp{E^{x}}\exp{E^{y}}$. The first result will follow from the commutator between $H_{x,y}^{c}$ and $\sum_{d=2}^{N}(E_{d1}^{x})\otimes \sum_{k=2}^{N}E_{b,1}^{x}$. Using \eqref{eq:comgl}, the bilinearity and associativity of the Kronecker product and the bilinearity of the brackets we obtain 
	&\left[\left(\sum_{d=2}^{N}E_{d1}^{x}\otimes\sum_{k=2}^{N}E_{k1}^{y}\right), \sum_{a,b=1}^{N}\left(E_{g_{c}(b)a}^{x}\otimes E_{g_{c}(a)b}^{y} -E_{aa}^{x}\otimes E_{bb}^{y}\right)\right]

@@

	\sum_{d,k=2}^{N}\sum_{a,b=1}^{N}\left\{\left((E_{da}^{x}\delta_{g_{c}(b)1}-E_{g_{c}(b)1}^{x}\delta_{ad})-(E_{da}^{y}\delta_{a1}-E_{a1}^{y}\delta_{da})\right)\right. \\ \otimes&\left. \left((E_{kb}^{y}\delta_{g_{c}(a)1}-E_{g_{c}1}^{y}\delta_{kb})-(E_{kb}^{y}\delta_{b1}-E_{b1}^{y}\delta_{kb})\right)\right\}
	\sum_{d,k=2}^{N}\sum_{a,b=1}^{N}\left\{\left(E_{da}^{x}-E_{g_{c}(b)1}^{x}-E_{da}^{x}+E_{a1}^{x}\right)\otimes\left(E_{kb}^{y}-E_{g_{c}(a)1}^{y}-E_{kb}^{y}+E_{b1}^{y}\right)\right\}
	\sum_{d,k=2}^{N}\sum_{a,b=1}^{N}\left\{\left(E_{a1}^{x}-E_{g_{c}(b)1}^{x}\right)\otimes \left(E_{b1}^{y}-E_{g_{c}(a)1}^{y}\right)\right\}
	\\=&0
where in the last equality we used the invertibility of the map $g_{c}(\cdot)$. \\
 The second result will follow from the commutator between $H_{x,y}^{m}$ and $\sum_{d=2}^{N}(E_{d1}^{x})\otimes \sum_{k=2}^{N}E_{b,1}^{x}$. The prof is similar and gives

@@

With this prove we answered to the second and third questions stated at the beginning of this section.
